A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Explanation of abuse of notation

% XXX handholding

\begin{proof}The direction~$(2) \Rightarrow (1)$ is immediate, as the internal
language of~$\Set[\TT]$ validates first-order intuitionistic logic and as it
validates the
axiom scheme~\eqref{eq:nullstellensatz} by Theorem~\ref{thm:nullstellensatz}.

>>>>

In stating the axiom scheme~\eqref{eq:nullstellensatz}, we are slightly abusing
notation. At face value, this axiom scheme would only make sense in the internal
language of~$\Set[\TT]$, where the generic model~$U_\TT$ actually lives.
However, here we are interpreting it in a purely syntactic context; when
writing~``$U_\TT$'', we actually mean the tautologous ``model'' in which any
sort of~$\TT$ is interpreted by the sort itself. For instance, if~$\sigma =
(\varphi \seq{x_1\!\?\!X_1,\ldots,x_n\!\?\!X_n} \psi)$ is a sequent,
then~$\speak{$\sigma$ holds for~$U_\TT$}$ is to be interpreted as the
formula~``$\forall x_1\?X_1\_ \ldots \forall x_n\?X_n\_ (\varphi \Rightarrow
\psi)$''.

\begin{proof}[Proof of Theorem~\ref{thm:characterization}]
The direction~$(2) \Rightarrow (1)$ is immediate, as the internal
language of~$\Set[\TT]$ validates first-order intuitionistic logic and as it
validates the
axiom scheme~\eqref{eq:nullstellensatz} by Theorem~\ref{thm:nullstellensatz}.
